```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
Below you find the scores of six students on the course 1.1 exam (social psychology) and the course 1.3 exam (statistics). Calculate the covariance between the exam scores of course 1.1 and course 1.3.

```{r, echo = FALSE}
Students <- 1:6
Exam_Course_1.1 <- c(7.5, 6.2, 5.2, 8.2, 9.2, 6.9)
Exam_Course_1.3 <- c(6.8, 5.4, 7.6, 7.6, 8.4, 4.7)

table <- cbind(Students, Exam_Course_1.1, Exam_Course_1.3)
kable(table, col.names = c("Students", "Exam Course 1.1", "Exam Course 1.3"))
```


Solution
========
```{r, echo = F}
Students <- 1:6
Exam_Course_1.1 <- c(7.5, 6.2, 5.2, 8.2, 9.2, 6.9)
Exam_Course_1.3 <- c(6.8, 5.4, 7.6, 7.6, 8.4, 4.7)
table <- cbind(Students, Exam_Course_1.1, Exam_Course_1.3)

product_dev11_dev13 <- c("(7.5 ‐ 7.2)(6.8 ‐ 6.75)", "(6.2 ‐ 7.2)(5.4 ‐ 6.75)", "(5.2 ‐ 7.2)(7.6 ‐ 6.75)", "(8.2 ‐ 7.2)(7.6 ‐ 6.75)", "(9.2 ‐ 7.2)(8.4 ‐ 6.75)", "(6.9 ‐ 7.2)(4.7 ‐ 6.75)")
answer_table <- cbind(table, product_dev11_dev13)
Sum <- c("", 43.20, 40.50, 4.43)
Mean <- c("", 7.2, 6.75, 0.738)
table <- rbind(answer_table, Sum, Mean)
kable(table, col.names = c("Students", "Exam Course 1.1", "Exam Course 1.3", "Product
deviation 1.1 – deviation 1.3"))
```

The mean is calculated by summing the scores on the exam and dividing this sum by the number of participants:

Mean Exam 1.1 = $\frac{43.20}{6} = 7.20$

Mean Exam 1.3 = $\frac{40.50}{6} = 6.75$


The covariance is calculated by summing the product of the deviation scores and divide this by N:
Covariance Exam 1.1, Exam 1.3: $Cov_{E1.1, E1.3} \frac{4.43}{6}=0.738$


Meta-information
================
exname: eur-descriptive-108-en
extype: num
exsolution: 0.738
extol: 0.01
exsection: Descriptive statistics/Summary Statistics/Bivariate statistics/Covariance
exextra[ID]: 83983
exextra[Type]: Calculate
exextra[Program]: Calculater
exextra[Language]: English
exextra[Level]: Statistical Literacy
