```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
Below you see the item variances of 12 items that together form a test to measure performance anxiety. The variance of the total score is 52.5. How many parallel items have to be added to get a reliability of .8?

```{r, echo=FALSE}
library(knitr)
library(exams)
Items <- 1:6
Variance <- c(1.50, 2.10, 1.20, 0.80, 1.00, 1.30, 2.10, 2.20, 2.50, 0.90, 1.20, 1.70)
table <- cbind(Items, Variance)
kable(table)
```
Use the following formulas:


$Alpha = (k / (k-1)) \times ( 1 - ∑S^2_i / S^2_x)$

$n = (Rxx-revised \times (1-Rxx-original))/(Rxx-original \times (1- Rxx-revised))$

Where Rxx-revised is the alfa you want to obtain and Rxx-original the reliability you originally had.

Answerlist
----------
* 20
* 8
* 7
* 19


Solution
========
The sum of the variances is 18.5. The reliability of the test is $12 \div 11 \times (1-18.5 \div 52.2)=.706$. 
Spearman-Brown formula can be used to calculate the lengthening factor n. This n is: $.23 \div .14=1.662$. 
When we product this value with 12, this is 19.9. This means that 8 items have to be added.

Answerlist
----------
* False
* True
* False
* False


Meta-information
================
exname: eur-reliability-209-en
extype: schoice
exsolution: 0100
exsection: Reliability/Analysis/Cronbach's alpha
exextra[Type]: Calculate
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy
exshuffle: TRUE
