```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```


Question
========
A PhD student at the institute of Psychology investigates the effect of gender in video modelling on the accuracy on a later task in which the participants have to perform a similar task as was explained in the video by a male or female model. From a meta study he learned that he may expect a main effect for gender: both male and female students learn more from male video models than from female video models. The effect-size in this meta-study was .80. Based on this effect-size the PhD makes a power calculation and decides that he needs 18 participants in each of the two conditions. 

Below you see the descriptive statistics the PhD student got from SPSS.

```{r, echo=FALSE}
library(knitr)
Group <- c("Male model", "Female model")
Mean <- c(20, 20)
SD <- c(1.8, 1.7)
n <- c(18, 18)
table <- cbind(Group, Mean, SD, n)
kable(table)
```

The reliability of the accuracy scores of the PhD student turned out to be .64.
Calculate the effect-size of the data using these descriptive data from the study of the PhD student. Round to 2 decimals.


Solution
========
The formula for the effect-size is: $d = \frac {x̄m - x̄f}{sp}$. Since both groups consist of 18 people the pooled standard deviation is simply the 
average of the two standard deviations. The pooled standard deviation is $sp = \sqrt {\frac{1.8^2 + 1.7^2}{2}} = 1.75$.
So the effect-size (Cohen's d) is $d = \frac{6.3 - 5.2}{1.75} = .629 = .63$


Meta-information
================
exname: eur-inferential_statistics-208-en
extype: num
exsolution: 0.63
extol: 0
exsection: Inferential Statistics/Effect size/Cohen's d, Reliability/Analysis/Cronbach's alpha
exextra[Type]: Calculate
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy
