```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
Below you find the scores of six students on the course 1.1 exam (social psychology) and the course 1.3 exam (statistics). Calculate the correlation between the exam scores of course 1.1 and course 1.3.

```{r, echo = FALSE}
Students <- 1:6
Exam_Course_1.1 <- c(7.5, 6.2, 5.2, 8.2, 9.2, 6.9)
Exam_Course_1.3 <- c(6.8, 5.4, 7.6, 7.6, 8.4, 4.7)

table <- cbind(Students, Exam_Course_1.1, Exam_Course_1.3)
kable(table, col.names = c("Students", "Exam Course 1.1", "Exam Course 1.3"))
```


Solution
========
```{r, echo = F}
Students <- 1:6
Exam_Course_1.1 <- c(7.5, 6.2, 5.2, 8.2, 9.2, 6.9)
Exam_Course_1.3 <- c(6.8, 5.4, 7.6, 7.6, 8.4, 4.7)
table <- cbind(Students, Exam_Course_1.1, Exam_Course_1.3)

squared_dev11 <- c("(7.5 ‐ 7.2)(7.5 ‐ 7.2)", "(6.2 ‐ 7.2)(6.2 ‐ 7.2)", "(5.2 ‐ 7.2)(5.2 ‐ 7.2)", "(8.2 ‐ 7.2)(8.2 ‐ 7.2)", "(9.2 ‐ 7.2)(9.2 ‐ 7.2)", "(6.9 ‐ 7.2)(6.9 ‐ 7.2)")
squared_dev13 <- c("(6.8 ‐ 6.75)(6.8 ‐ 6.75)", "(5.4 ‐ 6.75)(5.4 ‐ 6.75)", "(7.6 ‐ 6.75)(7.6 ‐ 6.75)", "(7.6 ‐ 6.75)(7.6 ‐ 6.75)", "(8.4 ‐ 6.75)(8.4 ‐ 6.75)", "(4.7 ‐ 6.75)(4.7 ‐ 6.75)")
product_dev11_dev13 <- c("(7.5 ‐ 7.2)(6.8 ‐ 6.75)", "(6.2 ‐ 7.2)(5.4 ‐ 6.75)", "(5.2 ‐ 7.2)(7.6 ‐ 6.75)", "(8.2 ‐ 7.2)(7.6 ‐ 6.75)", "(9.2 ‐ 7.2)(8.4 ‐ 6.75)", "(6.9 ‐ 7.2)(4.7 ‐ 6.75)")
answer_table <- cbind(table, squared_dev11, squared_dev13, product_dev11_dev13)
Sum <- c("", 43.20, 40.50, 10.18, 10.20, 4.43)
Mean <- c("", 7.20, 6.75,1.697, 1.699, 0.738)
table <- rbind(answer_table, Sum, Mean)
kable(table, col.names = c("Students", "Exam Course 1.1", "Exam Course 1.3", "Squared Deviation 1.1", "Squared Deviation 1.3", "Product deviation 1.1 – deviation 1.3"))
```

The mean is calculated by summing the scores on the exam and dividing this sum by the number of participants:

Mean Exam 1.1 = $\frac{43.20}{6} = 7.20$

Mean Exam 1.3 = $\frac{40.50}{6} = 6.75$


The covariance is calculated by summing the product of the deviation scores and divide this by N:

Covariance Exam 1.1, Exam 1.3: $Cov_{E1.1, E1.3} \frac{4.43}{6}=0.738$

The correlation is calculated by dividing the covariance by the product of the standard deviations.

The standard deviation is calculated by taking the square root of the variance:

Standard deviation $SD_{Exam 1.1} = \sqrt{1.697} = 1.303$ 

Standard deviation $SD_{Exam 1.3} = \sqrt{1.699} = 1.304$

Correlation Exam 1.1, Exam 1.3: $Cor_{E1.1, E1.3} = \frac{0.738}{1.303 \times 1.304}=.435$.


Meta-information
================
exname: eur-descriptive-109-en
extype: num
exsolution: .435
extol: 0.01
exsection: Descriptive statistics/Summary Statistics/Bivariate statistics/Correlation
exextra[Type]: Calculate
exextra[Program]: Calculater
exextra[Language]: English
exextra[Level]: Statistical Literacy
