```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```
Question
========
Below you find the observed scores on two parallel forms of a depression scale consisting of 8 items scored on a 5‐point Likert scale.

```{r, echo=FALSE}
library(knitr)
Participant <- 1:6
Form1 <- c(17,21,14,28,32,24)
Form2 <- c(19,23,11,24,34,21)
table <- cbind(Participant, Form1, Form2)
kable(table)
```

Calculate the reliability of depression scale using the alternate forms estimate of reliability.


Solution
========
The reliability of the depression scale can be estimated by calculating the correlation between the two alternative forms. The correlation is: $r_{F1,F2}$ = $\frac{38.67}{\sqrt{37.89 \times 46.67}} = .920$


Meta-information
================
exname: eur-reliability-101-en
extype: num
exsolution: .920
extol: 0
exsection: Reliability/Analysis/Parallel forms
exextra[Type]: Calculation
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy