```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
In four different studies a regression analysis with one predictor is conducted. Consider the t-tests of the regression coefficient in the four different regression models below.
Which of the four different t-tests has the smallest p-value?

```{r, echo=FALSE}
library(knitr)
Model <- c("I", "II", "III", "IV")
t_test <- c("t(29) = -1.3", "t(29) = 3.3", "t(299) = 1.3", "t(299) = -3.3")
table <- cbind(Model, t_test)
kable(table)
```

Answerlist
----------
* Model I
* Model II
* Model III
* Model IV


Solution
========
Model IV is correct. In general, larger t-values, regardless of whether it's a positive or negative value, are accompanied by smaller p-values. The sample size also has an influence. The same t-value (as in models II and IV) has a smaller associated p-value in a larger sample. So, according to this logic, the correct answer is model IV. The t-value and sample size (as shown by the df in the parentheses) are the largest here.

Answerlist
----------
* False
* False
* False
* True


Meta-information
================
exname: eur-inferential_statistics-215-en
extype: schoice
exsolution: 0001
exsection: Inferential Statistics/NHST/p-value, Inferential Statistics/NHST/Test statistic/t-statistic
exextra[Type]: Interpreting output
exextra[Program]: 
exextra[Language]: English
exextra[Level]: Statistical Literacy
