```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```


Question
========
Below, the responses of 4 people on 5 variables are shown. What are the rounded total scores (I to IV) when only the people who gave at least 3 answers are included? In SPSS this would be the function: rnd(means.3(v1 to v5) $\times$ 5).


```{r, echo=FALSE}
library(knitr)
ID <- c(1, 2, 3, 4)
V1 <- c(1, 3, 1, 3)
V2 <- c("...", "...", 2, 2)
V3 <- c("...", "...", 2, 2)
V4 <- c(2, "...", 3, 1)
V5 <- c(3, 2, "...", 1)
Total <- c("(I)", "(II)", "(III)", "(IV)")
table <- cbind(ID, V1, V2, V3, V4, V5, Total)
kable(table)
```

Answerlist
----------
* (I) 10, (II) missing, (III) 10 en (IV) 9
* (I) missing, (II) missing, (III) missing, (IV) 9
* (I) 6, (II) missing, (III) 8, (IV) 9
* (I) missing, (II) missing, (III) 10, (IV) 9


Solution
========
"(I) 10, (II) missing, (III) 10 en (IV) 9" is correct. For each person with at least 3 scores, you replace the missings by their mean score. For person 1 this makes: $1+2+3 \div 3 = 2$, so the scores are: 1, 2, 2, 2, 3 so a total score of 10. Person 2 is excluded, so “missing”, person 3 gets $8 \div 4 = 2$ to replace the missing, so the scores are 1, 2, 2, 3, 2 and the total score is 10. Person 4 has a total score of 9.

Answerlist
----------
* True
* False
* False
* False


Meta-information
================
exname: eur-descriptive-202-en
extype: schoice
exsolution: 1000
exsection: Descriptive statistics/Summary Statistics/Measures of Location, Descriptive statistics/Summary Statistics/Measures of Location/Mean
exextra[Type]: Calculate
exextra[Program]: 
exextra[Language]: English
exextra[Level]: Statistical Literacy
exshuffle: TRUE