```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
Below you see the variance-covariance matrix of three variables (V1 to V3). Calculate Cronbach’s alpha:

```{r, echo=FALSE}
library(knitr)
Variable <- c("V1", "V2", "V3")
V1 <- c(332, 165, 159)
V2 <- c("", 545, 235)
V3 <- c("", "", 336)
table <- cbind(Variable, V1, V2, V3)
kable(table)
```

Use the formula:


$Cronbach's Alpha = (k / (k-1)) \times ∑C_{ij} / S^2_x$

Answerlist
----------
* .21
* .47
* .72
* .78


Solution
========
We calculate the sum of the covariance and double it: $2 \times (165+159+235)=2 \times 559=1118$. 
For the variance of the total score we add the item variances: $1118+332+545+336=2331$. 
Cronbach's alpha then becomes: $3 \div 2 \times 1118 \div 2331=.72$

Answerlist
----------
* False
* False
* True
* False


Meta-information
================
exname: eur-reliability-208-en
extype: schoice
exsolution: 0010
exsection: Reliability/Analysis/Cronbach's alpha
exextra[ID]: 519f6
exextra[Type]: Calculate
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy
exshuffle: TRUE
