```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
In the following study we want to know how 100 “PvdA”+”VVD” voters feel about the party they voted for at the moment.

Calculate the Chi-square.

```{r, echo = FALSE}
Positive <- c(10, 20)
Negative <- c(30, 40)
table <- rbind(Positive, Negative)
colnames(table) <- c("PvdA", "VVD")
kable(table, caption = "Voted")
```

Answerlist
----------
* $\chi^2 = 1.14$
* $\chi^2 = 0.86$
* $\chi^2 = 0.79$
* $\chi^2 = 0.68$


Solution
========
The correct answer is 0.79.

Answerlist
----------
* This answer is incorrect
* This answer is incorrect
* This is the correct answer!
* This answer is incorrect


Meta-information
================
exname: eur-inferential_statistics-116-en
extype: schoice
exsolution: 0010
exsection: Inferential Statistics/NHST/Test statistic/Chi-squared
exextra[ID]: 59ff8
exextra[Type]: Calculation
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy
exshuffle: FALSE
