```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```
Question
========
Below you can find the observed scores on a depression scale with a one‐week interval.High scores indicate high levels of depression.

```{r, echo=FALSE}
library(knitr)
Participant <- 1:6
Form1 <- c(17,21,14,28,32,24)
Form2 <- c(19,23,11,24,34,21)
table <- cbind(Participant, Form1, Form2)
kable(table)
```

Calculate the test‐retest reliability. To decrease your work: 
$s^2_{1st} = 37.06$, $s^2_{2nd} = 54.56$ and $c_{1st,2nd} = 37.89$.


Solution
========
The test‐retest reliability is equal to the correlation between the two scores on the two administrations. This correlation is:  $r_{F1,F2}$ = $\frac{37.89}{\sqrt{37.06 \times 54.56}} = .843$.


Meta-information
================
exname: eur-reliability-102-en
extype: num
exsolution: .843
extol: 0.005
exsection: Reliability/Analysis/Test-retest
exextra[Type]: Calculation
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy