```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
A psychologist runs an ANCOVA with the dependent variable Y, the between-subject factor 'group' (1, 2, 3) and the covariate X with a mean of 110. This results in the following SPSS output:

```{r, echo=FALSE}
library(knitr)
parameter <- c("Intercept", "X", "Group=1", "Group=2", "Group=3")
B <- c(22.961, 1.139, 0.191, 5.008, "0(a)")
Std.Error <- c(6.313, 0.282, 1.878, 1.831, "...")
t <- c(3.637, 4.031, 0.102, 2.735, "...")
Sig <- c(.001, "0.000", ".920", .011, "...")
LowerboundCI <- c(9.984, 0.558, -3.669, 1.244, "...")
UpperboundCI <- c(35.939, 1.719, 4.051, 8.773, "...")
Partial_Eta <- c(.337, .385, "0.000", .223, "...")
table <- cbind(B, Std.Error, t, Sig, LowerboundCI, UpperboundCI, Partial_Eta)
kable(table)
```

What can be inferred about the adjusted mean of group 3 from the above table?

Answerlist
----------
* It does not differ from 0 statistically
* It equals 22.961 + 1.139 × 110
* It is significantly lower than the adjusted mean of group 1
* Nothing can be inferred about the adjusted mean of group 3, because it is the reference group.


Solution
========
The adjusted mean is the mean of a group when the covariate has its mean value. In other words, it is the mean of a group when adjusted for the covariate. The B-values in the table represent the difference between the adjusted mean of the relevant group and the adjusted mean of the reference group.

You can get the adjusted mean of group 3 by writing out the regression formula and entering a 0 for each of the other groups (or the dummies). For the covariate, enter the mean value (in this case 110). This is what you see at answer B.

Data for group 3 is missing as they are the reference group. Furthermore, the B-value for group 1 does indeed represent the difference between group 1 and the reference group (in this case group 3), but the table shows that this difference is not significant (p = .920).

Answerlist
----------
* False
* True
* False
* False


Meta-information
================
exname: eur-inferential_statistics-219-en
extype: schoice
exsolution: 0100
exsection: Inferential Statistics/Regression/Equation, Inferential Statistics/Regression/Dummies, Inferential Statistics/Regression/Simple linear regression
exextra[Type]: Interpreting output
exextra[Program]: 
exextra[Language]: English
exextra[Level]: Statistical Literacy
