```{r, echo = FALSE, results = "hide"}
#Load package
library(knitr)
```

Question
========
A researcher wants to know whether children who frequently use headphones have worse hearing than children who never use headphones. The higher the score on a hearing test, the better the hearing. The reliability of a hearing test is .81. In the table below, the means and standard deviations of the two groups are given. What would be the effect size Cohen’s d, $d_{XT}$, if the hearing test were perfectly reliable?


```{r, echo=FALSE}
library(knitr)
Condition <- c("Headphones", "No headphones")
Mean <- c(10, 11.25)
SD <- c(2, 3)
N <- c(30, 30)
table <- cbind(Condition, Mean, SD, N)
kable(table)
```

Answerlist
----------
* .405
* .490
* .545
* .556


Solution
========
First you use: 
 $d_{xO} = (x̄_{O1} -x̄_{O2}) \div √ ((S^2_{O1}+S^2_{O2}) \div 2)$ to calculate $d_{Xo}$. 

This makes $(11.25 - 10) \div √((9 + 4) \div 2)=1.25 \div √6.5 = (1.25 ) \div (2.5495) = 0.490$. 

Then you use:
$d_{X_O} = d_{X_T} \times √R_{XX}$

To calculate $d_{X_T}$, this makes $0.409 \div √0.81 = 0.409 \div 0.9 = 0.545$.

Answerlist
----------
* False
* False
* True
* False


Meta-information
================
exname: eur-inferential_statistics-202-en
extype: schoice
exsolution: 0010
exsection: Inferential Statistics/Effect size/Cohen's d
exextra[Type]: Calculate
exextra[Program]: Calculator
exextra[Language]: English
exextra[Level]: Statistical Literacy
exshuffle: TRUE